\documentclass{book}
\usepackage[margins=0.25in]{geometry}

\begin{document}
\tableofcontents
\newpage
\addcontentsline{toc}{section}{Pot Stickers}
\section*{Pot Stickers}
\subsection*{Ingredients}
\begin{itemize}
\item
$\frac{1}{2}$ pound ground pork/chicken/turkey
\item
$\frac{1}{4}$ cup finely chopped scallions
\item
2 tablespoons finely chopped red bell pepper
\item
1 egg, lightly beaten
\item
2 teaspoons ketchup
\item
1 teaspoon yellow mustard
\item
2 teaspoons Worcestershire sauce
\item
1 teaspoon light brown sugar
\item
$1 \frac{1}{2}$ teaspoons kosher salt
\item
$\frac{1}{2}$ teaspoon freshly ground black pepper
\item
$\frac{1}{4}$ teaspoon cayenne pepper
\item
35 to 40 small wonton wrappers
\item
Water, for sealing wontons
\item
3 to 4 tablespoons vegetable oil, for frying
\item
$1 \frac{1}{3}$ cups of chicken stock, divided
\end{itemize}
\subsection*{Instructions}
\begin{enumerate}
\item
Combine the first 11 ingredients in a medium-size mixing bowl (meat through cayenne). Set aside.
\item
To form the dumplings, remove 1 wonton wrapper from the package, covering the others with a damp cloth. Brush 2 of the edges of the wrapper lightly with water. Place 1/2 rounded teaspoon of the pork mixture in the center of the wrapper. Fold over, seal edges, and shape as desired. Set on a sheet pan and cover with a damp cloth. Repeat procedure until all of the filling is gone.
\item
Heat a 12-inch saute pan over medium heat. Brush with vegetable oil once hot. Add 8 to 10 potstickers at a time to the pan and cook for 2 minutes, without touching. Once the 2 minutes are up, gently add 1/3 cup chicken stock to the pan, turn the heat down to low, cover, and cook for another 2 minutes. Remove wontons to a heatproof platter and place in the warm oven. Clean the pan in between batches by pouring in water and allowing the pan to deglaze. Repeat until all the wontons are cooked. Serve immediately.
\end{enumerate}
\newpage
\addcontentsline{toc}{section}{Turtle Pecan Cheesecake}
\section*{Turtle Pecan Cheesecake}
\subsection*{Ingredients}
\subsubsection*{Cake}
\begin{itemize}
\item
2(8 oz.) cups chrushed chocolate cookies or vanilla wafers
\item
$\frac{1}{4}$ cups butter, melted
\item
3 (8 oz.) pkgs. cream cheese, softened
\item
1 cup sugar
\item
$1\frac{1}{2}$ Tablespoon all-purpse flour
\item
$\frac{1}{4}$ teaspoon salt
\item
3 eggs
\item
2 Tablespoons Half & Half
\item
1 cup pecans, chopped
\end{itemize}
\subsubsection*{Caramel Topping}
\begin{itemize}
\item
$\frac{1}{2}$ (14 oz.) bag caramel candies
\item
$\frac{1}{3}$ cup whipping cream
\end{itemize}
\subsubsection*{Chocolate Topping}
\begin{itemize}
\item
1 (4 oz.) pkg. German sweet chocolate
\item
1 teaspoon butter
\item
2 Tablespoon whipping cream
\end{itemize}
\subsection*{Instructions}
\subsubsection*{Cake}
Preheat oven to 450 degrees, combine cooke crumbs and butter. Press onto bottom of spring-form pan. Beat cream cheese in large bowl until creamy. Add sugar, flour, salt and vanilla. Mix well, Add eggs one at a time, beating well after each addition. Blend in cream. Poer over crust, bake 10 minutes, then reduce overn temp to 200 degrees. Continue baking 35 to 40 minutes or until set. Loosen cake from the rim of the spring-form pan. Cool before removing the rim of the pan. Drizzel with caramel topping and chocloate topping. Refigerate, sprinkle with chpped pecans just before serving.
\subsubsection*{Caramel Topping}
In a small saucepan combine caramels and cream. Stir over low heat until melted and smooth.
\subsubsection*{Chocolate Topping}
Combine in small sauce pan. Stir over low heat until smooth before using.
\newpage
\addcontentsline{toc}{section}{Apple Tort}
\section*{Apple Tort}
\subsection*{Ingredients}
\begin{itemize}
\item
$1\frac{1}{2}$ cups apples, diced small
\item
1 egg, beaten
\item
$\frac{1}{2}$ cups English Walnuts, chopped
\item
1 cup white sugar
\item
1 cup flour
\item
1 teaspoon baking soda
\end{itemize}
\subsection*{Instructions}
Mix soda with flour and sugar. Add resot of ingredients and keep stirring until moisture from apples make a nice batter. Pour batter in a $9 \times 9$ inch greashed pan. Bake for 30 minutes in 350 degree oven.
\newpage
\addcontentsline{toc}{section}{Cream Puff Dessert}
\section*{Cream Puff Dessert}
\subsection*{Ingredients}
\begin{itemize}
\item
1 cup water
\item
1 stick margarine
\item
1 cup flour
\item
4 eggs
\item
1 (8 oz.) pkg. cream cheese
\item
$3 \frac{1}{2}$ cups milk
\item
2 small pkg. instant vanilla pudding
\end{itemize}
\subsection*{Instructions}
Bring to boil, water & margarine. Add flour. Remove from heat, stir until it forms a ball, add egg one at a time, spread in greased jelly roll pan. Bake 20-25 minutes at 400 degrees. Press down and cool. Cream the cream cheese and add milk a little at a time. Add pudding, beat until thick pour over crust top with fruit in season or drizzel with chocolate syrup.
\newpage
\addcontentsline{toc}{section}{Cinnamon Coffeecake}
\section*{Cinnamon Coffeecake}
\subsection*{Ingredients}
\begin{itemize}
\item
$2\frac{1}{2}$ cup sifted flour
\item
1 cup brown sugar
\item
$\frac{3}{4}$ cup granulated sugar
\item
$\frac{2}{3}$ cup cooking oil
\item
2 teaspoons ground cinnamon
\item
$\frac{1}{2}$ cup chopped nuts (pecans or walnuts)
\item
1 egg
\item
$\frac{1}{2}$ teaspoon salt
\item
1 cup buttermilk
\item
1 teaspoon baking soda
\item
1 teaspoon baking powder
\end{itemize}
\subsection*{Instructions}
\begin{numerize}
\item
Combine four, brown sugar and granulated sugar and mix well.
\item
Add oil to dr ingredients: mix until crumbly. 
\item
Take $1\frac{1}{2}$ cups of this mixture, and put into another bowl.
\item
Add cinnamon and nuts to the $1\frac{1}{2}$ cup mixture.
\item
Take half of this mixture and prinkle into two $8\times11$ inch pans that been greased (you can use an $11\times13$ inch pan).
\item
Add egg, buttermilk, baking soda, baking powder, and solt, to the resot of the one bowl of dry ingredients.
\item
Mix well with electric beater.
\item
Pour batter over the mixture in pans. Then take remaining cinnamon mmixture and prinkle on the top.
\item
Bake in 325 degree oven for 45 minutes or until a toothpick omes out clean.
\end{numerize}
\newpage
\addcontentsline{toc}{section}{Italian Cream Cake}
\section*{Italian Cream Cake}
\subsection*{Ingredients}
\subsubsection*{Cake}
\begin{itemize}
\item
1 stick butter or margarine
\item
$\frac{1}{2}$ cup shortening
\item
2 cups sugar
\item
5 egg yolks
\item
2 cups flour, sifted
\item
1 teaspoon baking soda
\item
pinch salt
\item
1 cup buttermilk
\item
1 teaspoon vanilla
\item
1 cup coconut
\item
1 cup chopped nuts
\item
5 egg whites
\end{itemize}
\subsubsection*{Frosting}
\begin{itemize}
\item
1 (8 oz.) pkg. cream cheese, softened
\item
1 teaspoon vanilla
\item
1 (16 oz.) lb. powdered sugar
\item
1 stick butter or margarine, softened
\end{itemize}
\subsection*{Instuctions}
\subsubsection*{Cake}
\begin{numerize}
\item
Preheate oven to 350 degrees.
\item
Cream butter or margarine and shortening.
\item
Add sugar and beat.
\item
Add egg yolks, beat.
\item
Sift four, baking soda and salt. Add this alternately with buttermilk.
\item
Add vanilla, coconut and nuts.
\item
Beat egg whites until stiff, fold into mixture.
\item
Grease three 9 inch pans, line the sides with wax paper or grease and four entire pans.
\item
Bake in preheated oven for 25 to 30 minutes. Cool before frosting.
\end{numerize}
\subsubsection{Frosting}
\begin{numerize}
\item
Cream together and frost cake, ready to serve.
\end{numerize}
\newpage
\addcontentsline{toc}{section}{Granny Ruth's Ginger Bread}
\section*{Granny Ruth's Ginger Bread}
\subsection*{Ingredients}
\begin{itemize}
\item
$1\frac{1}{2}$ cups sugar
\item
$\frac{1}{2}$ cup corn oil
\item
$\frac{1}{2}$ cup molasses
\item
$\frac{3}{4}$ cup sweet milk
\item
2 eggs
\item
2 teaspoons baking powder
\item
1 teaspoon baking soda
\item
$\frac{1}{4}$ teaspoon salt
\item
6 tablespoons of ginger
\end{itemize}
\subsection*{Instructions}
\begin{numerize}
\item
Mix sugar, corn oil, molasses, and sweet milk in a mixing bowl and mix until all ingredients are combined.
\item
Add eggs one at a time to create an emulsion.
\item
Add the baking soda and poder, salt, and ginger.
\item
Fill a bowl full of flour and make an indentation to por the mixture in and stir until it looks like really moist playdough.
\item
Preheat oven to 375.
\item
Make a cookie shape and place on a cookie sheet.
\item
Bake for ten minutes if needed add five more.
\end{numerize}
\newpage
\addcontentsline{toc}{section}{Cinnamon Rolls}
\section*{Cinnamon Rolls}
\subsection*{Ingredients}
\subsubsection*{Dough}
\begin{itemize}
\item
$\frac{1}{4}$ ounce package of yeast
\item
$\frac{1}{2}$ cup warm water
\item
$\frac{1}{2}$ cup scalded milk
\item
$\frac{1}{4}$ cup sugar
\item
$\frac{1}{3}$ cup butter
\item
1 teaspoon salt
\item
1 egg
\item
$3 \frac{1}{2}$ to 4 cups of all-purpose flour
\end{itemize}
\subsubsection*{Filling}
\begin{itemize}
\item
8 ounces light brown sugar, around 1 cup
\item
1 tablespoon ground cinnamon
\item
Pinch of salt
\item
$\frac{3}{4}$ ounce unsalted butter, melted, around $1 \frac{1}{2}$ tablespoons
\end{itemize}
\subsubsection*{Glaze}
\begin{itemize}
\item
1 package cream cheese, softened
\item
$\frac{1}{4}$ stick butter, softened
\item
$\frac{1}{2}$ teaspoon vanilla extract
\item
$1\frac{1}{2}$ cups sifted confectioners' sugar
\item
$\frac{1}{8}$ teaspoon salt
\end{itemize}
\subsection*{Directions}
\begin{numerize}
\item
heat oven to 350.
\item
In a small bowl, dissolve yeast in warm water and set aside. In a large bowl mix milk, sugar, melted butter, salt and egg.
\item
Add 2 cups of flour and mix until smooth.
\item
Add yeast mixture.
\item
Mix in remaining flour until dough is easy to handle.
\item
Knead dough on a lightly floured surface for 5 to 10 minutes.
\item
Place in well-greased bowl, cover and let rise until doubled in size, usually 1 to $1 \frac{1}{2}$ hours.
\item
When doubled in size, punch down dough.
\item
Roll out on a floured surface into a 15X9 ince rectangle.
\item
Spread melted butter all over dough.
\item
Mix sugar and cinnamon and sprinkle over buttered dough. Sprinkle with walnuts, pecans, or raisins if desired.
\item
Beginning at the 15 inch side, role up dough and pinch edge together to seal. Cut into 12 to 15 slices.
\item
Coat the bottom of baking pan with butter and sprinkle with sugar place cinnamon roll slices close together in the pan and let rise until dough is doubled, about 45 minutes.
\item
Bake for about 30 minutes or until golden brown.
\item
Meanwhile, mix cream cheese, butter, powdered sugar, salt, and vanilla. Spread over slightly cooled rolls.
\end{numerize}
\newpage
\end{document}
